---
title: "Final Project"
author: "Cypress Marrs, Briana Cervantes"
date: "12/3/2021"
output:
  html_document:
    toc: true 
    toc_float: true 
    toc_depth: 6
    theme: yeti
    highlight: textmate
    code_folding: "hide"
    css: style.css
editor_options: 
  markdown: 
    wrap: 72
---

![eNJine
Logo](https://raw.githubusercontent.com/bri-ne/MUSA508-Final/main/otherimagesMD/enjine.jpg)

# ENGINEERING A BETTER COMMUTE

If you have ever felt like New Jersey trains needed work, you are not
wrong. In January 2019, stations across the New Jersey transit system
experienced the equivalent of 614 days (about 1 year 8 months)' worth of
delays.

![ALT
TEXT](https://static01.nyt.com/images/2018/08/09/nyregion/09njtransit1/merlin_141973050_e60da41c-1e46-4a4b-b59e-f23c41f77251-superJumbo.jpg)

But what if you could know your train was running late before it was
running late?

With eNJine, you can do just that. No more rushing, only to wait. No
more missing your connection. No more being late. At eNJine, our data
scientists are dedicated to engineering a better commute for you.

Our beta testing has focused on proving the feasibility of using machine
learning to improve commuting. Currently, eNJine can predict whether
trains will be departing within two minutes of their scheduled departure
times two hours ahead.

![Michael Scott struggles to get on a moving freight
train](https://thumbs.gfycat.com/AngelicComplexBoutu-size_restricted.gif)

Our model works because we understand how New Jersey transit works.

Below, you can see how train delays vary on days of the week and at
certain stops. With this and other insight, we dial into exactly what
causes New Jersey trains to be late, so you don't have to.

## GOALS FOR CODE AND CODE BELOW------

-   is it late over 2 mins y/n LOGISTiC

model put ins

-   lag time

-   time of day (at least two hours out)

-   line

-   station pickup (diff stations will be treated as a cat variable)

-   weather data

model outputs

-   is the train going to be late over 2 mins. at pickup station? Y/N

lines we'll be working with

Graphics - deliverable

-   Y/N outcomes for any variables

Codewise to do, next steps:

-   ~~choose two lines~~

-   \~merge the weather\~

    -   \~use this as a numeric variable at first\~

-   ~~merge stop location~~

    -   \~each stop as cat variable\~

-   at least get the code logistic regression

-   last step visuals

-   last last step revise, feat engineer

# SETUP -----

```{r initial, include=FALSE, warning=FALSE, message=FALSE}
# Libraries -----------------
library(tidyr)
library(dplyr)
library(lubridate)
library(sf)
library(tidycensus)
library(tidyverse)
library(tigris)
library(riem)
library(gridExtra)
library(knitr)
library(kableExtra)
library(caret)
library(knitr) 
library(pscl)
library(plotROC)
library(gtsummary) #for table cause broom always f's everything up
library(pROC)
library(tibble)
library(cowplot)
## FOR MAPS ~~
library(RColorBrewer)
library(ggmap)  
library(maps)
library(mapdata)



options(tigris_class = "sf")
source("https://raw.githubusercontent.com/urbanSpatial/Public-Policy-Analytics-Landing/master/functions.r")


palette6 <- c("#260a03", "#a81010", "#f8cd12", "#f2fdff", "#93afdc", "#0c0e1d" )

palette5 <- c("#260a03", "#a81010", "#f8cd12", "#f2fdff", "#93afdc", "#0c0e1d" )

palette4 <- c("#a81010", "#f8cd12", "#93afdc", "#0c0e1d" )

palette3 <- c("#a81010", "#f8cd12", "#93afdc")

palette2 <- c("#260a03", "#a81010")

palette2b <- c( "#260a03", "#f8cd12")

plotTheme2 <-function(base_size = 12, title_size = 18) {
  theme(
    panel.background =element_blank(), 
    text = element_text( color = "#0c0e1d", family="Helvetica"),
    plot.title = element_text(size = title_size, colour = "#0c0e1d", family="Helvetica", face="bold"), 
    plot.subtitle = element_text(face="italic", family="Helvetica", colour = "#0c0e1d"),
    plot.caption = element_text(hjust=0, colour = "#0c0e1d", family="Helvetica"),

    axis.ticks.y = element_line(color = "grey80", size = 0.1),
    plot.background =element_blank(),
    
    panel.grid.major.x   = element_line("grey80", size =0.1 ),
    panel.grid.major.y   =element_line("grey80", size = 0.05),
    panel.grid.minor = element_blank(),
    panel.border = element_rect(colour = "#93afdc", fill=NA, size=4),
    #panel.spacing = unit(c(2,2,2,2), "cm"),
    strip.background = element_rect(fill = "#93afdc", color = "#93afdc"),
    strip.text = element_text(size=12,color ="#0c0e1d", family="Helvetica"),
    axis.title = element_text(size=12, color ="#0c0e1d", family="Helvetica",  face="italic"),
    axis.text = element_text(size=10, color ="#0c0e1d", family="Helvetica",),
    
    legend.background = element_blank(),
    legend.title = element_text(colour = "#0c0e1d", face = "italic", family="Helvetica"),
    legend.text = element_text(colour = "#0c0e1d", face = "italic", family="Helvetica"),
    strip.text.x = element_text(size = 14, family="Helvetica", colour = "#0c0e1d")
  )
}


plotTheme3 <-function(base_size = 12, title_size = 18) {
  theme(
    panel.background=element_rect(fill = "#93afdc", color = "#f2fdff"), 
    text = element_text( color = "#0c0e1d", family="Helvetica"),
    plot.title = element_text(size = title_size, colour = "#0c0e1d", family="Helvetica", face="bold"), 
    plot.subtitle = element_text(face="italic", family="Helvetica", colour = "#0c0e1d"),
    plot.caption = element_text(hjust=0, colour = "#0c0e1d", family="Helvetica"),

    axis.ticks.y = element_line(color = "grey80", size = 0.1),
    plot.background =element_blank(),
    
    panel.grid.major.x   = element_line("grey80", size =0.1 ),
    panel.grid.major.y   =element_line("grey80", size = 0.05),
    panel.grid.minor = element_blank(),
    panel.border =element_blank(),
    #panel.spacing = unit(c(2,2,2,2), "cm"),
    strip.background = element_rect(fill = "#f2fdff", color = "#f2fdff"),
    strip.text = element_text(size=12,color ="#0c0e1d", family="Helvetica"),
    axis.title = element_text(size=12, color ="#0c0e1d", family="Helvetica",  face="italic"),
    axis.text = element_text(size=10, color ="#0c0e1d", family="Helvetica",),
    
    legend.background = element_blank(),
    legend.title = element_text(colour = "#0c0e1d", face = "italic", family="Helvetica"),
    legend.text = element_text(colour = "#0c0e1d", face = "italic", family="Helvetica"),
    strip.text.x = element_text(size = 14, family="Helvetica", colour = "#f2fdff")
  )
}



mapTheme2<-function(base_size = 12, title_size = 16) {
  theme(
    text = element_text( color = "#0c0e1d", family="Helvetica"),
    plot.title = element_text(size = title_size,colour = "#0c0e1d", family="Helvetica"),
    plot.subtitle=element_text(face="italic", family="Helvetica"),
    plot.caption=element_text(hjust=0),
    axis.ticks = element_blank(),
    panel.background = element_blank(),axis.title = element_blank(),
    axis.text = element_blank(),
    axis.title.x = element_blank(),
    axis.title.y = element_blank(),
    panel.grid.minor = element_blank(),
    panel.border = element_rect(colour = "#93afdc", fill=NA, size=2),
    strip.text.x = element_text(size = 14, color="#0c0e1d", family="Helvetica"),
    strip.background  = element_rect(fill="#93afdc", color="#93afdc"))
}

```

## Bringing in the RAW Data ----

```{r datatrains,  warning=FALSE, message=FALSE, include=FALSE, echo=TRUE, results='hide'}
# Data -----------
root.dir = "https://raw.githubusercontent.com/urbanSpatial/Public-Policy-Analytics-Landing/master/DATA/"
jan2019 <- read.csv("https://raw.githubusercontent.com/bri-ne/MUSA508-Final/main/data/2019_01.csv?token=AVOS24NFX2PEGNUZQUPRNY3BXYPQY")
feb2019 <- read.csv("https://raw.githubusercontent.com/bri-ne/MUSA508-Final/main/data/2019_02.csv?token=AVOS24PUUJDM2PW36N5T6K3BXYPQ4")
mar2019 <- read.csv("https://raw.githubusercontent.com/bri-ne/MUSA508-Final/main/data/2019_03.csv?token=AVOS24MRII4RKEMYGNWWUSDBXYPQ6")
weather.Data <- 
  riem_measures(station = "EWR", date_start = "2019-01-01", date_end = "2019-05-01")
```

```{r wrangledate,  warning=FALSE, message=FALSE, include=FALSE, echo=TRUE, results='hide'}
njtransitdf <- rbind(jan2019, feb2019, mar2019)


njtransitdf <- njtransitdf %>% 
  mutate(scheduled_time_dt = as_datetime(scheduled_time),
         actual_time_dt = as_datetime(actual_time),
         delay_dt = seconds(as.integer(delay_minutes*60)), 
         intervalhour = floor_date(scheduled_time_dt, unit= "hour"),
         week = week(intervalhour)) %>%
  na.omit(delay_dt)

```

```{r stations,  warning=FALSE, message=FALSE, include=FALSE, echo=TRUE, results='hide'}
stoplocations <- read.csv("https://raw.githubusercontent.com/bri-ne/MUSA508-Final/main/Rail_Stations_of_NJ_Transit.csv?token=AVSVPEVU7X6RXZP3RNOK2CLBW7VZO")

stoplocations <- stoplocations %>%rename(X = "ï..X")%>%st_as_sf(coords = c("X", "Y"), crs =3424, agr = "constant") 

#stoplocations <- stoplocations %>%st_as_sf(coords = c("X", "Y"), crs =3424, agr = "constant") 
```

## New Approach- Lines Specific Models

```{r template,  warning=FALSE, message=FALSE, include=FALSE, echo=TRUE, results='hide'}

## Filters down to Week 1- 10
## Train on 8 test on 2 weeks 
train.template <- 
  filter(njtransitdf, week %in% c(1: 10))%>%filter(line == "Bergen Co. Line " | line == "Gladstone Branch")



#### TRYING TO GET A FEAT WHERE IF PREV STOP WAS LATE, NEXT STOP WILL BE LATE ------

## JUST BERGEN, *Not Grouped By Anything* 

berg <- train.template%>%filter(line == "Bergen Co. Line ")

  # grouping by all the things we want to investigate later, so we don't lose detail: 
  ### specifically adding train_id, so that we can nest in tibble
bergInterval <- berg%>%group_by(train_id, stop_sequence, from, to, intervalhour)%>%summarize(late = mean(delay_dt, na.rm=T))%>%arrange(intervalhour)%>% 
                                                                                mutate(lagHour = dplyr::lag(late,1),
                                                                                         lag2Hours = dplyr::lag(late,2),
                                                                                         lag3Hours = dplyr::lag(late,3),
                                                                                         lag4Hours = dplyr::lag(late,4),
                                                                                         lag12Hours = dplyr::lag(late,12),
                                                                                         lag1day = dplyr::lag(late,24),
                                                                                        lag1week = dplyr::lag(late, 168)) ## This is a Study Panel    


## JUST GLADSTONE, *Not Grouped By Anything* 

glad <- train.template%>%filter(line == "Gladstone Branch")

  # grouping by all the things we want to investigate later, so we don't lose detail: 
gladInterval <- glad%>%group_by(train_id, stop_sequence, from, to, intervalhour)%>%summarize(late = mean(delay_dt, na.rm=T))%>%arrange(intervalhour)%>%
                                                                                mutate(lagHour = dplyr::lag(late,1),
                                                                                         lag2Hours = dplyr::lag(late,2),
                                                                                         lag3Hours = dplyr::lag(late,3),
                                                                                         lag4Hours = dplyr::lag(late,4),
                                                                                         lag12Hours = dplyr::lag(late,12),
                                                                                         lag1day = dplyr::lag(late,24),
                                                                                        lag1week = dplyr::lag(late, 168)) ## This is a Study Panel

### MAKING NA 0

gladInterval[c("lagHour", "lag2Hours", "lag3Hours", "lag4Hours", "lag12Hours","lag1day", "lag1week")][is.na(gladInterval[c("lagHour", "lag2Hours", "lag3Hours", "lag4Hours", "lag12Hours","lag1day", "lag1week")])] <- 0 


bergInterval[c("lagHour", "lag2Hours", "lag3Hours", "lag4Hours", "lag12Hours","lag1day", "lag1week")][is.na(bergInterval[c("lagHour", "lag2Hours", "lag3Hours", "lag4Hours", "lag12Hours","lag1day", "lag1week")])] <- 0 



gladInterval <- gladInterval%>%mutate(lateM = late/60,
                              hour= hour(intervalhour),
                              daynumeric= wday(intervalhour),
                              week = week(intervalhour),
                              weekday = weekdays(intervalhour),
            late_catagorical = ifelse(late < minutes(1), "ontime", ifelse(late < minutes(4), "few_minutes", "late")))

bergInterval <- bergInterval%>%mutate(lateM = late/60,
                              hour= hour(intervalhour),
                              daynumeric= wday(intervalhour),
                              week = week(intervalhour),
                              weekday = weekdays(intervalhour),
            late_catagorical = ifelse(late < minutes(1), "ontime", ifelse(late < minutes(4), "few_minutes", "late")))


```

```{r stationsGEOMS, warning=FALSE, message=FALSE, include=FALSE, echo=TRUE, results='hide'}

#### MAKING A COPY b/c THIS SHIT KEEPS NOT WORKIGN

bergInterval2 <- bergInterval
gladInterval2 <- gladInterval


### THIS can be moved to a more appropriate spot later, but for now: 

  ## First, merge with stop data:
  

station_id <- unique(stoplocations$STATION_ID)

  ### Getting the names the same 
      
      ## GLAD ~~~~

gladInterval2$from<-replace(gladInterval2$from, gladInterval2$from == "Hoboken", "Hoboken Terminal")
gladInterval2$to<-replace(gladInterval2$to, gladInterval2$to == "Hoboken", "Hoboken Terminal")

gladInterval2$from<-replace(gladInterval2$from, gladInterval2$from == "Secaucus Upper Lvl", "Secaucus Junction Upper Level")
gladInterval2$to<-replace(gladInterval2$to, gladInterval2$to == "Secaucus Upper Lvl", "Secaucus Junction Upper Level")

gladstops <- unique(gladInterval2$from)
length(gladstops)

gladID <- stoplocations%>%
  filter(STATION_ID %in% gladstops)
#lenght(gladID)

gladGEOM <- gladInterval%>%merge(gladID, by.x ="from", by.y="STATION_ID") 

      ## BERG ~~~


stoplocations <- stoplocations%>%mutate(STATION_ID = ifelse(COUNTY == "Orange, NY" & STATION_ID == "Middletown", "Middletown NY", STATION_ID))

bergInterval2$from<-replace(bergInterval2$from, bergInterval2$from == "Broadway Fair Lawn", "Broadway")
bergInterval2$from<-replace(bergInterval2$from, bergInterval2$from == "Glen Rock Boro Hall", "Glen Rock-Boro Hall")
bergInterval2$from<-replace(bergInterval2$from, bergInterval2$from == "Hoboken", "Hoboken Terminal")
bergInterval2$from<-replace(bergInterval2$from, bergInterval2$from == "Radburn Fair Lawn", "Radburn")
bergInterval2$from<-replace(bergInterval2$from, bergInterval2$from == "Ramsey Main St", "Ramsey")
bergInterval2$from<-replace(bergInterval2$from, bergInterval2$from == "Ramsey Route 17", "Rte 17 Ramsey")
bergInterval2$from<-replace(bergInterval2$from, bergInterval2$from == "Secaucus Lower Lvl", "Secaucus Junction Lower Level")


bergInterval2$to<-replace(bergInterval2$to, bergInterval2$to == "Broadway Fair Lawn", "Broadway")
bergInterval2$to<-replace(bergInterval2$to, bergInterval2$to == "Glen Rock Boro Hall", "Glen Rock-Boro Hall")
bergInterval2$to<-replace(bergInterval2$to, bergInterval2$to == "Hoboken", "Hoboken Terminal")
bergInterval2$to<-replace(bergInterval2$to, bergInterval2$to == "Radburn Fair Lawn", "Radburn")
bergInterval2$to<-replace(bergInterval2$to, bergInterval2$to == "Ramsey Main St", "Ramsey")
bergInterval2$to<-replace(bergInterval2$to, bergInterval2$to == "Ramsey Route 17", "Rte 17 Ramsey")
bergInterval2$to<-replace(bergInterval2$to, bergInterval2$to == "Secaucus Lower Lvl", "Secaucus Junction Lower Level")

bergstops <- unique(bergInterval2$from)

length(bergstops)
bergID <- stoplocations%>%
  filter(STATION_ID %in% bergstops)
length(bergID)

bergGEOM <- bergInterval%>%merge(bergID, by.x ="from", by.y="STATION_ID")
bergGEOM <-bergGEOM%>%st_as_sf( crs =3424, agr = "constant")
gladGEOM <-gladGEOM%>%st_as_sf( crs =3424, agr = "constant")

```

## Getting Stop Lag

No weather yet.

Steps - Just doing this for one train first? - get only regression
variables - make stop lag - divide train and test - run regression

### Stop Lag & Prepping Models:

```{r stoplag,  warning=FALSE, message=FALSE, include=FALSE, echo=TRUE, results='hide'}

## Remaking Model 3 with STOP LAG: Calling it 3b: GLADSTONE LINE PROTOTYPE

### Adding our Y variable -----

    ##GLAD
gladModel<- gladInterval%>%mutate(y2_numeric = ifelse(late < minutes(2), 0, 1),
                                  y2 = ifelse(late < minutes(2), "no", "yes"),
                                  y5_numeric = ifelse(late < minutes(5), 0, 1),
                                 y5 = ifelse(late < minutes(5), "no", "yes"),
                                 tuesWed.binary = ifelse(weekday == "Tuesday"|weekday == "Wednesday", 1, 0),
                                  toPenn.binary =  ifelse(to == "New York Penn Station", 1, 0))

    ##BERG
bergModel<- bergInterval%>%mutate(y2_numeric = ifelse(late < minutes(2), 0, 1),
                                  y2 = ifelse(late < minutes(2), "no", "yes"),
                                  y5_numeric = ifelse(late < minutes(5), 0, 1),
                                 y5 = ifelse(late < minutes(5), "no", "yes"),
                                 friWed.binary = ifelse(weekday == "Friday"|weekday == "Wednesday", 1, 0),
                                  toPenn.binary =  ifelse(to == "New York Penn Station", 1, 0),
                                 toSigStop = ifelse(to == "Broadway Fair Lawn"| to == "Mahwah" | to == "Ramsey Main St"| to == "Waldwick", 0, 1))



### Subsetting the DF -----



    ## GLAD
gladModel<-gladModel%>%dplyr::select(
                                        train_id,
                                        stop_sequence,
                                        from, 
                                        to,
                                        late,
                                        week,
                                        weekday, 
                                        hour,
                                        lagHour, 
                                        lag2Hours, 
                                        lag3Hours, 
                                        y2, 
                                        intervalhour,
                                        y2_numeric,
                                        tuesWed.binary,
                                        toPenn.binary)

    ## BERG

bergModel<-bergModel%>%dplyr::select(
                                        train_id,
                                        stop_sequence,
                                        from, 
                                        to,
                                        late,
                                        week,
                                        weekday, 
                                        hour,
                                        lagHour, 
                                        lag2Hours, 
                                        lag3Hours, 
                                        y2, 
                                        intervalhour,
                                        y2_numeric,
                                        friWed.binary,
                                        toSigStop)




## THIS WORKS NO TIBBLE NEEDED::::STOP LAG:::::: ----

    ## GLAD

gladModel.good <-gladModel%>%group_by(train_id)%>%arrange(stop_sequence)%>%mutate(onestoplag = dplyr::lag(late),
                                                                          twostoplag = dplyr::lag(late,2))%>%ungroup()

gladModel.good[c("onestoplag","twostoplag")][is.na(gladModel.good[c("onestoplag","twostoplag")])] <- 0 



    ## BERG

bergModel.good <-bergModel%>%group_by(train_id)%>%arrange(stop_sequence)%>%mutate(onestoplag = dplyr::lag(late), twostoplag = dplyr::lag(late))%>%ungroup()

bergModel.good[c("onestoplag","twostoplag")][is.na(bergModel.good[c("onestoplag","twostoplag")])] <- 0 

### Splitting train and test THIS IS NO WEATHER----

  ## GLAD
  
gladModel.good <- mutate(gladModel.good, week_numeric = as.numeric(week))

set.seed(2121)
gladTrain <- filter(gladModel.good, week < 9)
gladTest <- filter(gladModel.good, week >= 9)



  ## BERG


bergModel.good <- mutate(bergModel.good, week_numeric = as.numeric(week))

set.seed(2121)
bergTrain <- filter(bergModel.good, week < 9)

bergTest <- filter(bergModel.good, week >= 9)


```

### Getting Weather Data

#### Weather Data

```{r dataweather,  warning=FALSE, message=FALSE, include=FALSE, echo=TRUE, results='hide'}
# Data -----------
weather.Panel <-  
  weather.Data %>%
    mutate_if(is.character, list(~replace(as.character(.), is.na(.), "0"))) %>% 
    replace(is.na(.), 0) %>%
    mutate(intervalhour = ymd_h(substr(valid, 1, 13))) %>%
    mutate(dotw = wday(intervalhour, label=TRUE)) %>%
    group_by(intervalhour) %>%
    summarize(Temperature = max(tmpf),
              Percipitation = sum(p01i),
              Wind_Speed = max(sknt)) %>%
    mutate(Temperature = ifelse(Temperature == 0, 42, Temperature)) 

#Bring in other data sources and join in legible ways that will make data useable 


```

```{r weatherMERGE,  warning=FALSE, message=FALSE, include=FALSE, echo=TRUE, results='hide'}

## MERGING

    ## GLAD

glad.weather.panel <- merge(x= gladModel.good, y= weather.Panel, by= 'intervalhour', all.x= T)

glad.weather.panel <- 
glad.weather.panel%>% 
      group_by(intervalhour) %>% 
    arrange(intervalhour) %>% 

    mutate(
            lag1Hourwind = dplyr::lag(Wind_Speed,1),
           lag2Hourswind = dplyr::lag(Wind_Speed,2),  ##taking note from the pres today about windspeed 
           lag3Hourswind = dplyr::lag(Wind_Speed,3),
           lag4Hourswind = dplyr::lag(Wind_Speed,4),
           lag12Hourswind = dplyr::lag(Wind_Speed,12),
           lag1daywind = dplyr::lag(Wind_Speed,24))%>%mutate(
           SQRTlag1Hourwind = sqrt(lag1Hourwind),
           SQRTlag2Hourswind = sqrt(lag2Hourswind),  ##taking note from the pres today about windspeed 
           SQRTlag3Hourswind = sqrt(lag3Hourswind),
           SQRTlag4Hourswind = sqrt(lag4Hourswind),
           SQRTlag12Hourswind = sqrt(lag12Hourswind),
           SQRTlag1daywind = sqrt(lag1daywind)) %>% 
   ungroup()


    ## BERG

berg.weather.panel <- merge(x= bergModel.good, y= weather.Panel, by= 'intervalhour', all.x= T)

berg.weather.panel <- 
berg.weather.panel%>% 
      group_by(intervalhour) %>% 
    arrange(intervalhour) %>% 

    mutate(lag1Hourwind = dplyr::lag(Wind_Speed,1),
           lag2Hourswind = dplyr::lag(Wind_Speed,2),  ##taking note from the pres today about windspeed 
           lag3Hourswind = dplyr::lag(Wind_Speed,3),
           lag4Hourswind = dplyr::lag(Wind_Speed,4),
           lag12Hourswind = dplyr::lag(Wind_Speed,12),
           lag1daywind = dplyr::lag(Wind_Speed,24)) %>%mutate(
           SQRTlag1Hourwind = sqrt(lag1Hourwind),
           SQRTlag2Hourswind = sqrt(lag2Hourswind),  ##taking note from the pres today about windspeed 
           SQRTlag3Hourswind = sqrt(lag3Hourswind),
           SQRTlag4Hourswind = sqrt(lag4Hourswind),
           SQRTlag12Hourswind = sqrt(lag12Hourswind),
           SQRTlag1daywind = sqrt(lag1daywind))%>% 
   ungroup()



### Making all new NAs ZERO ~~~~

glad.weather.panel[c("lag1Hourwind",  "lag2Hourswind", "lag3Hourswind", "lag4Hourswind", "lag12Hourswind", "lag1daywind", "SQRTlag1Hourwind",  "SQRTlag2Hourswind", "SQRTlag3Hourswind", "SQRTlag4Hourswind", "SQRTlag12Hourswind", "SQRTlag1daywind")][is.na(glad.weather.panel[c( "lag1Hourwind", "lag2Hourswind", "lag3Hourswind", "lag4Hourswind", "lag12Hourswind", "lag1daywind", "SQRTlag1Hourwind",  "SQRTlag2Hourswind", "SQRTlag3Hourswind", "SQRTlag4Hourswind", "SQRTlag12Hourswind", "SQRTlag1daywind")])] <- 0 

berg.weather.panel[c("lag1Hourwind",  "lag2Hourswind", "lag3Hourswind", "lag4Hourswind", "lag12Hourswind", "lag1daywind", "SQRTlag1Hourwind",  "SQRTlag2Hourswind", "SQRTlag3Hourswind", "SQRTlag4Hourswind", "SQRTlag12Hourswind", "SQRTlag1daywind")][is.na(berg.weather.panel[c( "lag1Hourwind", "lag2Hourswind", "lag3Hourswind", "lag4Hourswind", "lag12Hourswind", "lag1daywind", "SQRTlag1Hourwind",  "SQRTlag2Hourswind", "SQRTlag3Hourswind", "SQRTlag4Hourswind", "SQRTlag12Hourswind", "SQRTlag1daywind")])] <- 0 


```

## Running Models

-   Model 1: Weather, Stoplag, Hourlag
-   Model 2: Weather and Stoplag
-   Model 3: Weather and Hourlag
-   Model 4: Stoplag and Houralg
-   Model 5: SqrootWeather, Stoplag and Houralg

```{r MODELs,  warning=FALSE, message=FALSE, include=FALSE, echo=TRUE, results='hide'}

## Gotta split again: 

### Splitting train and test ----


    ## GLAD

set.seed(2121)
gladTrainW <- filter(glad.weather.panel, week < 9)
gladTestW <- filter(glad.weather.panel, week >= 9)

    ## BERG

set.seed(2121)
bergTrainW <- filter(berg.weather.panel, week < 9)
bergTestW <- filter(berg.weather.panel, week >= 9)

```

```{r corrplots}
library(ggcorrplot)

numericVars <- 
  select_if(berg.weather.panel, is.numeric) %>% na.omit()

ggcorrplot(
  round(cor(numericVars), 1), 
  p.mat = cor_pmat(numericVars),
  colors = c("#25CB10", "white", "#FA7800"),
  type="lower",
  insig = "blank") +  
    labs(title = "Correlation across numeric variables") 

```

```{r runningthemodel}


#### Running the Model

    ## GLAD ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ 

        ## GLAD MODEL 1 ------------------        


gladModel1<- glm(y2_numeric ~ .,
                        data=glad.weather.panel %>% 
                          dplyr::select(y2_numeric,
                                        stop_sequence, 
                                        onestoplag,
                                        hour, 
                                        lagHour,
                                        lag2Hours,
                                        lag3Hours,
                                        toPenn.binary, 
                                        tuesWed.binary, 
                                        Wind_Speed,
                                        lag4Hourswind,   ## these are the only winds that were sig
                                        lag1daywind),  
                        family="binomial" (link="logit"))



gladsummary1.table <- tbl_regression(gladModel1, exponentiate = TRUE)

        ## GLAD MODEL 2 ------------------        


gladModel2<- glm(y2_numeric ~ .,
                        data=glad.weather.panel %>% 
                          dplyr::select(y2_numeric,
                                        stop_sequence, 
                                        onestoplag,
                                        hour, 
                                        toPenn.binary, 
                                        tuesWed.binary, 
                                        Wind_Speed,
                                        lag4Hourswind,   ## these are the only winds that were sig
                                        lag1daywind),  
                        family="binomial" (link="logit"))



gladsummary2.table <- tbl_regression(gladModel2, exponentiate = TRUE)



        ## GLAD MODEL 3 ------------------        


gladModel3<- glm(y2_numeric ~ .,
                        data=glad.weather.panel %>% 
                          dplyr::select(y2_numeric,
                                        stop_sequence,
                                        hour, 
                                        lagHour,
                                        lag2Hours,
                                        lag3Hours,
                                        toPenn.binary, 
                                        tuesWed.binary, 
                                        Wind_Speed,
                                        lag4Hourswind,   ## these are the only winds that were sig
                                        lag1daywind),  
                        family="binomial" (link="logit"))



gladsummary3.table <- tbl_regression(gladModel3, exponentiate = TRUE)





        ## GLAD MODEL 4 ------------------        


gladModel4<- glm(y2_numeric ~ .,
                        data=glad.weather.panel %>% 
                          dplyr::select(y2_numeric,
                                        stop_sequence, 
                                        onestoplag,
                                        hour, 
                                        lagHour,
                                        lag2Hours,
                                        lag3Hours,
                                        toPenn.binary, 
                                        tuesWed.binary),  
                        family="binomial" (link="logit"))



gladsummary4.table <- tbl_regression(gladModel4, exponentiate = TRUE)





        ## GLAD MODEL 5 ------------------        


gladModel5<- glm(y2_numeric ~ .,
                        data=glad.weather.panel %>% 
                          dplyr::select(y2_numeric,
                                        stop_sequence, 
                                        onestoplag,
                                        hour, 
                                        lagHour,
                                        lag2Hours,
                                        lag3Hours,
                                        toPenn.binary,
                                        SQRTlag1daywind,
                                        tuesWed.binary),  
                        family="binomial" (link="logit"))



gladsummary5.table <- tbl_regression(gladModel5, exponentiate = TRUE)
   
    ## BERG ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~


        ## BERG MODEL 1 ------------------


bergModel1<- glm(y2_numeric ~ .,
                        data=berg.weather.panel %>% 
                          dplyr::select(y2_numeric,
                                        stop_sequence, 
                                        onestoplag,
                                        hour, 
                                        toSigStop, ## the to.Pennbinary var was  colinar but the to isn't IDK why
                                        lagHour,
                                        lag2Hours,
                                        lag3Hours,
                                        friWed.binary, 
                                        Wind_Speed),  
                        family="binomial" (link="logit"))



bergsummary1.table <- tbl_regression(bergModel1, exponentiate = TRUE)



        ## BERG MODEL 2 ------------------


bergModel2<- glm(y2_numeric ~ .,
                        data=berg.weather.panel %>% 
                          dplyr::select(y2_numeric,
                                        stop_sequence, 
                                        onestoplag,
                                        hour, 
                                        toSigStop, ## the to.Pennbinary var was  colinar but the to isn't IDK why
                                        friWed.binary, 
                                        Wind_Speed),  
                        family="binomial" (link="logit"))



bergsummary22.table <- tbl_regression(bergModel2, exponentiate = TRUE)


        ## BERG MODEL 3 ------------------


bergModel3<- glm(y2_numeric ~ .,
                        data=berg.weather.panel %>% 
                          dplyr::select(y2_numeric,
                                        stop_sequence,
                                        hour, 
                                        toSigStop, ## the to.Pennbinary var was  colinar but the to isn't IDK why
                                        lagHour,
                                        lag2Hours,
                                        lag3Hours,
                                        friWed.binary, 
                                        Wind_Speed),  
                        family="binomial" (link="logit"))



bergsummary3.table <- tbl_regression(bergModel3, exponentiate = TRUE)



        ## BERG MODEL 4 ------------------


bergModel4<- glm(y2_numeric ~ .,
                        data=berg.weather.panel %>% 
                          dplyr::select(y2_numeric,
                                        #stop_sequence, ##<-- it's the same w/o these vars
                                        onestoplag,
                                        #hour, 
                                        toSigStop, ## the to.Pennbinary var was  colinar but the to isn't IDK why
                                        lagHour,
                                        lag2Hours,
                                        lag3Hours,
                                        friWed.binary),  
                        family="binomial" (link="logit"))



bergsummary4.table <- tbl_regression(bergModel4, exponentiate = TRUE)



        ## BERG MODEL 5 ------------------


bergModel5<- glm(y2_numeric ~ .,
                        data=berg.weather.panel %>% 
                          dplyr::select(y2_numeric,
                                        stop_sequence, 
                                        onestoplag,
                                        hour, 
                                        toSigStop, ## the to.Pennbinary var was  colinar but the to isn't IDK why
                                        lagHour,
                                        lag2Hours,
                                        lag3Hours,
                                        SQRTlag1Hourwind,
                                        SQRTlag1daywind,
                                        friWed.binary),  
                        family="binomial" (link="logit"))



bergsummary5.table <- tbl_regression(bergModel5, exponentiate = TRUE)


```

## Cross Validation

```{r CROSVAL, warning=FALSE, message=FALSE, include=FALSE, echo=TRUE, results='hide'}


#### Cross Validation 

ctrl <- trainControl(method = "cv", number = 100, classProbs=TRUE, summaryFunction=twoClassSummary)

##### GLAD -----

      #### GLAD 1 ----


gladModel1.vars <- colnames(gladTrainW %>%dplyr::select(
                                        stop_sequence, 
                                        onestoplag,
                                        hour, 
                                        lagHour,
                                        lag2Hours,
                                        lag3Hours,
                                        toPenn.binary, 
                                        tuesWed.binary, 
                                        Wind_Speed,
                                        lag4Hourswind,   ## these are the only winds that were sig
                                        lag1daywind))

gladcvFit1 <- caret::train(y2 ~ .,
                        data=gladTrainW %>%dplyr::select(all_of(gladModel1.vars), y2), ### in the book, they cv on all the data but i'm pretty sure it should just be train
                        method="glm", family="binomial",
                        metric="ROC", trControl = ctrl)

gladcvFit1.plot<- dplyr::select(gladcvFit1$resample, -Resample) %>%
  gather(metric, value) %>%
  left_join(gather(gladcvFit1$results[2:4], metric, mean)) %>%
  ggplot(aes(value)) + 
  geom_histogram(bins=35, fill = "#93afdc") +
  facet_wrap(~metric) +
  geom_vline(aes(xintercept = mean), colour = "#a81010", linetype = 3, size = 1.5) +
  scale_x_continuous(limits = c(0, 1)) +
  labs(x="Goodness of Fit", y="Count", title="Glad: MODEL 1 Goodness of Fit Metrics",
       subtitle = "Across-fold mean reprented as dotted lines",
       caption= " ") +
  plotTheme2()


      #### GLAD 2 ----


gladModel2.vars <- colnames(gladTrainW %>%dplyr::select(
                                        stop_sequence, 
                                        onestoplag,
                                        hour, 
                                        toPenn.binary, 
                                        tuesWed.binary, 
                                        Wind_Speed,
                                        lag4Hourswind,   ## these are the only winds that were sig
                                        lag1daywind))

gladcvFit2 <- caret::train(y2 ~ .,
                        data=gladTrainW %>%dplyr::select(all_of(gladModel2.vars), y2), ### in the book, they cv on all the data but i'm pretty sure it should just be train
                        method="glm", family="binomial",
                        metric="ROC", trControl = ctrl)

gladcvFit2.plot<- dplyr::select(gladcvFit2$resample, -Resample) %>%
  gather(metric, value) %>%
  left_join(gather(gladcvFit2$results[2:4], metric, mean)) %>%
  ggplot(aes(value)) + 
  geom_histogram(bins=35, fill = "#93afdc") +
  facet_wrap(~metric) +
  geom_vline(aes(xintercept = mean), colour = "#a81010", linetype = 3, size = 1.5) +
  scale_x_continuous(limits = c(0, 1)) +
  labs(x="Goodness of Fit", y="Count", title="Glad: MODEL 2 Goodness of Fit Metrics",
       subtitle = "Across-fold mean reprented as dotted lines",
       caption= " ") +
  plotTheme2()


      #### GLAD 3 ----


gladModel3.vars <- colnames(gladTrainW %>%dplyr::select(stop_sequence,
                                        hour, 
                                        lagHour,
                                        lag2Hours,
                                        lag3Hours,
                                        toPenn.binary, 
                                        tuesWed.binary, 
                                        Wind_Speed,
                                        lag4Hourswind,   ## these are the only winds that were sig
                                        lag1daywind))

gladcvFit3 <- caret::train(y2 ~ .,
                        data=gladTrainW %>%dplyr::select(all_of(gladModel3.vars), y2), ### in the book, they cv on all the data but i'm pretty sure it should just be train
                        method="glm", family="binomial",
                        metric="ROC", trControl = ctrl)

gladcvFit3.plot<- dplyr::select(gladcvFit3$resample, -Resample) %>%
  gather(metric, value) %>%
  left_join(gather(gladcvFit3$results[2:4], metric, mean)) %>%
  ggplot(aes(value)) + 
  geom_histogram(bins=35, fill = "#93afdc") +
  facet_wrap(~metric) +
  geom_vline(aes(xintercept = mean), colour = "#a81010", linetype = 3, size = 1.5) +
  scale_x_continuous(limits = c(0, 1)) +
  labs(x="Goodness of Fit", y="Count", title="Glad: MODEL 3 Goodness of Fit Metrics",
       subtitle = "Across-fold mean reprented as dotted lines",
       caption= " ") +
  plotTheme2()



      #### GLAD 4 ----


gladModel4.vars <- colnames(gladTrainW %>%dplyr::select(stop_sequence, 
                                        onestoplag,
                                        hour, 
                                        lagHour,
                                        lag2Hours,
                                        lag3Hours,
                                        toPenn.binary, 
                                        tuesWed.binary))

gladcvFit4<- caret::train(y2 ~ .,
                        data=gladTrainW %>%dplyr::select(all_of(gladModel4.vars), y2), ### in the book, they cv on all the data but i'm pretty sure it should just be train
                        method="glm", family="binomial",
                        metric="ROC", trControl = ctrl)

gladcvFit4.plot<- dplyr::select(gladcvFit4$resample, -Resample) %>%
  gather(metric, value) %>%
  left_join(gather(gladcvFit4$results[2:4], metric, mean)) %>%
  ggplot(aes(value)) + 
  geom_histogram(bins=35, fill = "#93afdc") +
  facet_wrap(~metric) +
  geom_vline(aes(xintercept = mean), colour = "#a81010", linetype = 3, size = 1.5) +
  scale_x_continuous(limits = c(0, 1)) +
  labs(x="Goodness of Fit", y="Count", title="Glad: MODEL 4 Goodness of Fit Metrics",
       subtitle = "Across-fold mean reprented as dotted lines",
       caption= " ") +
  plotTheme2()

      #### GLAD 5 ----


gladModel5.vars <- colnames(gladTrainW %>%dplyr::select(stop_sequence, 
                                        onestoplag,
                                        hour, 
                                        lagHour,
                                        lag2Hours,
                                        lag3Hours,
                                        toPenn.binary,
                                        SQRTlag1daywind,
                                        tuesWed.binary))

gladcvFit5 <- caret::train(y2 ~ .,
                        data=gladTrainW %>%dplyr::select(all_of(gladModel5.vars), y2), ### in the book, they cv on all the data but i'm pretty sure it should just be train
                        method="glm", family="binomial",
                        metric="ROC", trControl = ctrl)

gladcvFit5.plot<- dplyr::select(gladcvFit5$resample, -Resample) %>%
  gather(metric, value) %>%
  left_join(gather(gladcvFit5$results[2:4], metric, mean)) %>%
  ggplot(aes(value)) + 
  geom_histogram(bins=35, fill = "#93afdc") +
  facet_wrap(~metric) +
  geom_vline(aes(xintercept = mean), colour = "#a81010", linetype = 3, size = 1.5) +
  scale_x_continuous(limits = c(0, 1)) +
  labs(x="Goodness of Fit", y="Count", title="Glad: MODEL 5 Goodness of Fit Metrics",
       subtitle = "Across-fold mean reprented as dotted lines",
       caption= " ") +
  plotTheme2()















##### BERG -----

      #### BERG 1 ----


bergModel1.vars <- colnames(bergTrainW %>%dplyr::select(stop_sequence, 
                                        onestoplag,
                                        hour, 
                                        toSigStop, ## the to.Pennbinary var was  colinar but the to isn't IDK why
                                        lagHour,
                                        lag2Hours,
                                        lag3Hours,
                                        friWed.binary, 
                                        Wind_Speed))

bergcvFit1 <- caret::train(y2 ~ .,
                        data=bergTrainW %>%dplyr::select(all_of(bergModel1.vars), y2), ### in the book, they cv on all the data but i'm pretty sure it should just be train
                        method="glm", family="binomial",
                        metric="ROC", trControl = ctrl)

bergcvFit1.plot<- dplyr::select(bergcvFit1$resample, -Resample) %>%
  gather(metric, value) %>%
  left_join(gather(bergcvFit1$results[2:4], metric, mean)) %>%
  ggplot(aes(value)) + 
  geom_histogram(bins=35, fill = "#93afdc") +
  facet_wrap(~metric) +
  geom_vline(aes(xintercept = mean), colour = "#a81010", linetype = 3, size = 1.5) +
  scale_x_continuous(limits = c(0, 1)) +
  labs(x="Goodness of Fit", y="Count", title="BERG: MODEL 1 Goodness of Fit Metrics",
       subtitle = "Across-fold mean reprented as dotted lines",
       caption= " ") +
  plotTheme2()


      #### BERG 2 ----


bergModel2.vars <- colnames(bergTrainW %>%dplyr::select(
                                        stop_sequence, 
                                        onestoplag,
                                        hour, 
                                        toSigStop, ## the to.Pennbinary var was  colinar but the to isn't IDK why
                                        friWed.binary, 
                                        Wind_Speed))

bergcvFit2 <- caret::train(y2 ~ .,
                        data=bergTrainW %>%dplyr::select(all_of(bergModel2.vars), y2), ### in the book, they cv on all the data but i'm pretty sure it should just be train
                        method="glm", family="binomial",
                        metric="ROC", trControl = ctrl)

bergcvFit2.plot<- dplyr::select(bergcvFit2$resample, -Resample) %>%
  gather(metric, value) %>%
  left_join(gather(bergcvFit2$results[2:4], metric, mean)) %>%
  ggplot(aes(value)) + 
  geom_histogram(bins=35, fill = "#93afdc") +
  facet_wrap(~metric) +
  geom_vline(aes(xintercept = mean), colour = "#a81010", linetype = 3, size = 1.5) +
  scale_x_continuous(limits = c(0, 1)) +
  labs(x="Goodness of Fit", y="Count", title="BERG: MODEL 2 Goodness of Fit Metrics",
       subtitle = "Across-fold mean reprented as dotted lines",
       caption= " ") +
  plotTheme2()

      #### BERG 3 ----


bergModel3.vars <- colnames(bergTrainW %>%dplyr::select(
                                        stop_sequence,
                                        hour, 
                                        toSigStop, ## the to.Pennbinary var was  colinar but the to isn't IDK why
                                        lagHour,
                                        lag2Hours,
                                        lag3Hours,
                                        friWed.binary, 
                                        Wind_Speed))

bergcvFit3 <- caret::train(y2 ~ .,
                        data=bergTrainW %>%dplyr::select(all_of(bergModel3.vars), y2), ### in the book, they cv on all the data but i'm pretty sure it should just be train
                        method="glm", family="binomial",
                        metric="ROC", trControl = ctrl)

bergcvFit3.plot<- dplyr::select(bergcvFit3$resample, -Resample) %>%
  gather(metric, value) %>%
  left_join(gather(bergcvFit3$results[2:4], metric, mean)) %>%
  ggplot(aes(value)) + 
  geom_histogram(bins=35, fill = "#93afdc") +
  facet_wrap(~metric) +
  geom_vline(aes(xintercept = mean), colour = "#a81010", linetype = 3, size = 1.5) +
  scale_x_continuous(limits = c(0, 1)) +
  labs(x="Goodness of Fit", y="Count", title="BERG: MODEL 3 Goodness of Fit Metrics",
       subtitle = "Across-fold mean reprented as dotted lines",
       caption= " ") +
  plotTheme2()

      #### BERG 4 ----


bergModel4.vars <- colnames(bergTrainW %>%dplyr::select(
                                        #stop_sequence, ##<-- it's the same w/o these vars
                                        onestoplag,
                                        #hour, 
                                        toSigStop, ## the to.Pennbinary var was  colinar but the to isn't IDK why
                                        lagHour,
                                        lag2Hours,
                                        lag3Hours,
                                        friWed.binary))

bergcvFit4 <- caret::train(y2 ~ .,
                        data=bergTrainW %>%dplyr::select(all_of(bergModel4.vars), y2), ### in the book, they cv on all the data but i'm pretty sure it should just be train
                        method="glm", family="binomial",
                        metric="ROC", trControl = ctrl)

bergcvFit4.plot<- dplyr::select(bergcvFit4$resample, -Resample) %>%
  gather(metric, value) %>%
  left_join(gather(bergcvFit4$results[2:4], metric, mean)) %>%
  ggplot(aes(value)) + 
  geom_histogram(bins=35, fill = "#93afdc") +
  facet_wrap(~metric) +
  geom_vline(aes(xintercept = mean), colour = "#a81010", linetype = 3, size = 1.5) +
  scale_x_continuous(limits = c(0, 1)) +
  labs(x="Goodness of Fit", y="Count", title="BERG: MODEL 4 Goodness of Fit Metrics",
       subtitle = "Across-fold mean reprented as dotted lines",
       caption= " ") +
  plotTheme2()




      #### BERG 5 ----


bergModel5.vars <- colnames(bergTrainW %>%dplyr::select(
                                        stop_sequence, 
                                        onestoplag,
                                        hour, 
                                        toSigStop, ## the to.Pennbinary var was  colinar but the to isn't IDK why
                                        lagHour,
                                        lag2Hours,
                                        lag3Hours,
                                        SQRTlag1Hourwind,
                                        SQRTlag1daywind,
                                        friWed.binary))

bergcvFit5 <- caret::train(y2 ~ .,
                        data=bergTrainW %>%dplyr::select(all_of(bergModel5.vars), y2), ### in the book, they cv on all the data but i'm pretty sure it should just be train
                        method="glm", family="binomial",
                        metric="ROC", trControl = ctrl)

bergcvFit5.plot<- dplyr::select(bergcvFit5$resample, -Resample) %>%
  gather(metric, value) %>%
  left_join(gather(bergcvFit5$results[2:4], metric, mean)) %>%
  ggplot(aes(value)) + 
  geom_histogram(bins=35, fill = "#93afdc") +
  facet_wrap(~metric) +
  geom_vline(aes(xintercept = mean), colour = "#a81010", linetype = 3, size = 1.5) +
  scale_x_continuous(limits = c(0, 1)) +
  labs(x="Goodness of Fit", y="Count", title="BERG: MODEL 5 Goodness of Fit Metrics",
       subtitle = "Across-fold mean reprented as dotted lines",
       caption= " ") +
  plotTheme2()






```

### CV Plots

```{r cvplots}


plot_grid(gladcvFit1.plot, gladcvFit2.plot, gladcvFit3.plot, gladcvFit4.plot, gladcvFit5.plot, nrow=3, ncol=2)
plot_grid(bergcvFit1.plot, bergcvFit2.plot, bergcvFit3.plot, bergcvFit4.plot, bergcvFit5.plot, nrow=3, ncol=2)

```


## Predictions

```{r PREDICTIONS1, warning=FALSE, message=FALSE, include=FALSE, echo=TRUE, results='hide'}



### MODELS 1
#### Setting up Predictions FOR Weather, Stoplag, and Hourlag -----

    ## GLAD

gladtestProbs1 <- data.frame(Outcome = as.factor(gladTestW$y2_numeric),
                         Probs = predict(gladModel1, gladTestW, type="response"))

    ## BERG

bergtestProbs1 <- data.frame(Outcome = as.factor(bergTestW$y2_numeric),
                         Probs = predict(bergModel1, bergTestW, type="response"))



#### FIGURE OUT WHAT THRESH with plot and iterate fn -----




## TEST PROBS PLOT **MODEL 3cW -- to figure out what threh**


    ## GLAD ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~


 glad1<- ggplot(gladtestProbs1, aes(x = Probs, fill = as.factor(Outcome))) + 
  geom_density() +
  facet_grid(Outcome ~ .) +
  scale_fill_manual(values = palette2) +
  labs(x = "Late Over 2 Mins", y = "Density of probabilities",
       title = "GladStone Model 1: Distribution of Predicted Probabilities by Actual Outcome",
       caption= " ") +
  theme(strip.text.x = element_text(size = 18),
        legend.position = "none")+plotTheme2()

 
 gladtestProbs1.thresholds <- 
  iterateThresholds(data=gladtestProbs1, observedClass = Outcome, 
                    predictedProbs = Probs)

gladtestProbs1.thresholds<-gladtestProbs1.thresholds%>%arrange(Rate_TP,Rate_TN) ## 0.48 identified

gladtestProbs1 <- 
  gladtestProbs1 %>%
  mutate(predOutcome  = as.factor(ifelse(gladtestProbs1$Probs > 0.48 , 1, 0)))


gladauc1<-pROC::auc(gladtestProbs1$Outcome, gladtestProbs1$Probs) #0.7465


gladroc.1<- ggplot(gladtestProbs1, aes(d = as.numeric(Outcome), m = Probs)) +
  geom_roc(n.cuts = 50, labels = FALSE, colour = "#a81010") +
  style_roc(theme = theme_grey) +
  geom_abline(slope = 1, intercept = 0, size = 1.5, color = 'grey') +
  labs(title = "ROC Curve - GLAD Model 1", subtitle = paste("AUC:", round(gladauc1[1], digits=3)) )+plotTheme2()







    ## BERG ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~


 berg1<- ggplot(bergtestProbs1, aes(x = Probs, fill = as.factor(Outcome))) + 
  geom_density() +
  facet_grid(Outcome ~ .) +
  scale_fill_manual(values = palette2) +
  labs(x = "Late Over 2 Mins", y = "Density of probabilities",
       title = "BERG Model 1: Distribution of Predicted Probabilities by Actual Outcome",
       caption= " ") +
  theme(strip.text.x = element_text(size = 18),
        legend.position = "none")+plotTheme2()

 
 bergtestProbs1.thresholds <- 
  iterateThresholds(data=bergtestProbs1, observedClass = Outcome, 
                    predictedProbs = Probs)

bergtestProbs1.thresholds<-bergtestProbs1.thresholds%>%arrange(Rate_TP,Rate_TN) ## 0.55 identified

bergtestProbs1 <- 
  bergtestProbs1 %>%
  mutate(predOutcome  = as.factor(ifelse(bergtestProbs1$Probs > 0.55 , 1, 0)))





bergauc1 <- pROC::auc(bergtestProbs1$Outcome, bergtestProbs1$Probs) #0.7437


bergroc.1<- ggplot(bergtestProbs1, aes(d = as.numeric(Outcome), m = Probs)) +
  geom_roc(n.cuts = 50, labels = FALSE, colour = "#a81010") +
  style_roc(theme = theme_grey) +
  geom_abline(slope = 1, intercept = 0, size = 1.5, color = 'grey') +
  labs(title = "ROC Curve - BERG Model 1", subtitle = paste("AUC:", round(bergauc1[1], digits=3)))+plotTheme2()








#plot_grid(glad1, berg1, nrow = 2)





```

```{r PREDICTIONS2, warning=FALSE, message=FALSE, include=FALSE, echo=TRUE, results='hide'}


#### MODELS 2

#### Setting up Predictions FOR JUST Weather and Stoplag-----

    ## GLAD

gladtestProbs2 <- data.frame(Outcome = as.factor(gladTestW$y2_numeric),
                         Probs = predict(gladModel2, gladTestW, type="response"))

    ## BERG

bergtestProbs2 <- data.frame(Outcome = as.factor(bergTestW$y2_numeric),
                         Probs = predict(bergModel2, bergTestW, type="response"))



#### FIGURE OUT WHAT THRESH with plot and iterate fn -----




## TEST PROBS PLOT **MODEL 3cW -- to figure out what threh**


    ## GLAD ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~


 glad2<- ggplot(gladtestProbs2, aes(x = Probs, fill = as.factor(Outcome))) + 
  geom_density() +
  facet_grid(Outcome ~ .) +
  scale_fill_manual(values = palette2) +
  labs(x = "Late Over 2 Mins", y = "Density of probabilities",
       title = "GladStone Model 2: Distribution of Predicted Probabilities by Actual Outcome",
       caption= " na") +
  theme(strip.text.x = element_text(size = 18),
        legend.position = "none")+plotTheme2()

 
 gladtestProbs2.thresholds <- 
  iterateThresholds(data=gladtestProbs2, observedClass = Outcome, 
                    predictedProbs = Probs)

gladtestProbs2.thresholds<-gladtestProbs2.thresholds%>%arrange(Rate_TP,Rate_TN) ## 0.50 identified



gladtestProbs2 <- 
  gladtestProbs2 %>%
  mutate(predOutcome  = as.factor(ifelse(gladtestProbs2$Probs > 0.50 , 1, 0)))






gladauc2<-pROC::auc(gladtestProbs2$Outcome, gladtestProbs2$Probs) #0.7465


gladroc.2<- ggplot(gladtestProbs2, aes(d = as.numeric(Outcome), m = Probs)) +
  geom_roc(n.cuts = 50, labels = FALSE, colour = "#a81010") +
  style_roc(theme = theme_grey) +
  geom_abline(slope = 1, intercept = 0, size = 1.5, color = 'grey') +
  labs(title = "ROC Curve - Model GLAD 2", subtitle = paste("AUC:", round(gladauc2[1], digits=3)))+plotTheme2()







    ## BERG ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~


 berg2<- ggplot(bergtestProbs2, aes(x = Probs, fill = as.factor(Outcome))) + 
  geom_density() +
  facet_grid(Outcome ~ .) +
  scale_fill_manual(values = palette2) +
  labs(x = "Late Over 2 Mins", y = "Density of probabilities",
       title = "BERG Model 2: Distribution of Predicted \nProbabilities by Actual Outcome",
       caption= " ") +
  theme(strip.text.x = element_text(size = 18),
        legend.position = "none")+plotTheme2()

 
 bergtestProbs2.thresholds <- 
  iterateThresholds(data=bergtestProbs2, observedClass = Outcome, 
                    predictedProbs = Probs)

bergtestProbs2.thresholds<-bergtestProbs2.thresholds%>%arrange(Rate_TP,Rate_TN) ## 0.56 identified



bergtestProbs2<- 
  bergtestProbs2%>%
  mutate(predOutcome  = as.factor(ifelse(bergtestProbs2$Probs > 0.56 , 1, 0)))

bergauc2<-pROC::auc(bergtestProbs2$Outcome, bergtestProbs2$Probs) #0.7437


bergroc.2<- ggplot(bergtestProbs2, aes(d = as.numeric(Outcome), m = Probs)) +
  geom_roc(n.cuts = 50, labels = FALSE, colour = "#a81010") +
  style_roc(theme = theme_grey) +
  geom_abline(slope = 1, intercept = 0, size = 1.5, color = 'grey') +
  labs(title = "ROC Curve - BERG Model 2", subtitle = paste("AUC:", round(bergauc2[1], digits=3)))+plotTheme2()






#plot_grid(glad2, berg2, nrow = 2)





 berg2






```

```{r PREDICTIONS3, warning=FALSE, message=FALSE, include=FALSE, echo=TRUE, results='hide'}


### MODELS 3

#### Setting up Predictions FOR JUST Weather and Stoplag-----

    ## GLAD

gladtestProbs3 <- data.frame(Outcome = as.factor(gladTestW$y2_numeric),
                         Probs = predict(gladModel3, gladTestW, type="response"))

    ## BERG

bergtestProbs3 <- data.frame(Outcome = as.factor(bergTestW$y2_numeric),
                         Probs = predict(bergModel3, bergTestW, type="response"))



#### FIGURE OUT WHAT THRESH with plot and iterate fn -----




## TEST PROBS PLOT **MODEL 3cW -- to figure out what threh**


    ## GLAD ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~


 glad3<- ggplot(gladtestProbs3, aes(x = Probs, fill = as.factor(Outcome))) + 
  geom_density() +
  facet_grid(Outcome ~ .) +
  scale_fill_manual(values = palette2) +
  labs(x = "Late Over 2 Mins", y = "Density of probabilities",
       title = "GladStone Model 3: Distribution of Predicted Probabilities by Actual Outcome",
       caption= " ") +
  theme(strip.text.x = element_text(size = 18),
        legend.position = "none")+plotTheme2()

 
 gladtestProbs3.thresholds <- 
  iterateThresholds(data=gladtestProbs3, observedClass = Outcome, 
                    predictedProbs = Probs)

gladtestProbs3.thresholds<-gladtestProbs3.thresholds%>%arrange(Rate_TP,Rate_TN) ## 0.49 identified


gladtestProbs3 <- 
  gladtestProbs3 %>%
  mutate(predOutcome  = as.factor(ifelse(gladtestProbs3$Probs > 0.49 , 1, 0)))






gladauc3<-pROC::auc(gladtestProbs3$Outcome, gladtestProbs3$Probs) #0.7465




gladroc.3<- ggplot(gladtestProbs3, aes(d = as.numeric(Outcome), m = Probs)) +
  geom_roc(n.cuts = 50, labels = FALSE, colour = "#a81010") +
  style_roc(theme = theme_grey) +
  geom_abline(slope = 1, intercept = 0, size = 1.5, color = 'grey') +
  labs(title = "ROC Curve - GLAD Model 3", subtitle = paste("AUC:", round(gladauc3[1], digits=3)))+plotTheme2()







    ## BERG ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~


 berg3<- ggplot(bergtestProbs3, aes(x = Probs, fill = as.factor(Outcome))) + 
  geom_density() +
  facet_grid(Outcome ~ .) +
  scale_fill_manual(values = palette2) +
  labs(x = "Late Over 2 Mins", y = "Density of probabilities",
       title = "BERG Model 3: Distribution of Predicted Probabilities by Actual Outcome",
       caption= " ") +
  theme(strip.text.x = element_text(size = 18),
        legend.position = "none")+plotTheme2()

 
 bergtestProbs3.thresholds <- 
  iterateThresholds(data=bergtestProbs3, observedClass = Outcome, 
                    predictedProbs = Probs)

bergtestProbs3.thresholds<-bergtestProbs3.thresholds%>%arrange(Rate_TP,Rate_TN) ## 0.54 identified




bergtestProbs3 <- 
  bergtestProbs3 %>%
  mutate(predOutcome  = as.factor(ifelse(bergtestProbs3$Probs > 0.54 , 1, 0)))





bergauc3<-pROC::auc(bergtestProbs3$Outcome, bergtestProbs3$Probs) #0.7437



bergroc.3<- ggplot(bergtestProbs3, aes(d = as.numeric(Outcome), m = Probs)) +
  geom_roc(n.cuts = 50, labels = FALSE, colour = "#a81010") +
  style_roc(theme = theme_grey) +
  geom_abline(slope = 1, intercept = 0, size = 1.5, color = 'grey') +
  labs(title = "ROC Curve - BERG Model 3", subtitle = paste("AUC:", round(bergauc3[1], digits=3)))+plotTheme2()







#plot_grid(glad3, berg3, nrow = 2)












```

```{r PREDICTIONS4, warning=FALSE, message=FALSE, include=FALSE, echo=TRUE, results='hide'}

##MODELS 4


#### Setting up Predictions FOR JUST Weather and Stoplag-----

    ## GLAD

gladtestProbs4<- data.frame(Outcome = as.factor(gladTestW$y2_numeric),
                         Probs = predict(gladModel4, gladTestW, type="response"))

    ## BERG

bergtestProbs4 <- data.frame(Outcome = as.factor(bergTestW$y2_numeric),
                         Probs = predict(bergModel4, bergTestW, type="response"))



#### FIGURE OUT WHAT THRESH with plot and iterate fn -----




## TEST PROBS PLOT **MODEL 3cW -- to figure out what threh**


    ## GLAD ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~


 glad4 <- ggplot(gladtestProbs4, aes(x = Probs, fill = as.factor(Outcome))) + 
  geom_density() +
  facet_grid(Outcome ~ .) +
  scale_fill_manual(values = palette2) +
  labs(x = "Late Over 2 Mins", y = "Density of probabilities",
       title = "GladStone Model 4: Distribution of Predicted Probabilities by Actual Outcome",
       caption= "WEATHER has stop lags") +
  theme(strip.text.x = element_text(size = 18),
        legend.position = "none")+plotTheme2()

 
 gladtestProbs4.thresholds <- 
  iterateThresholds(data=gladtestProbs4, observedClass = Outcome, 
                    predictedProbs = Probs)

gladtestProbs4.thresholds<-gladtestProbs4.thresholds%>%arrange(Rate_TP,Rate_TN) ## 0.48 identified



gladtestProbs4 <- 
  gladtestProbs4 %>%
  mutate(predOutcome  = as.factor(ifelse(gladtestProbs4$Probs > 0.48 , 1, 0)))







gladauc4<- pROC::auc(gladtestProbs4$Outcome, gladtestProbs4$Probs) #0.7469
#0.7469


gladroc.4<- ggplot(gladtestProbs4, aes(d = as.numeric(Outcome), m = Probs)) +
  geom_roc(n.cuts = 50, labels = FALSE, colour = "#a81010") +
  style_roc(theme = theme_grey) +
  geom_abline(slope = 1, intercept = 0, size = 1.5, color = 'grey') +
  labs(title = "ROC Curve - GLAD Model 4", subtitle = paste("AUC:", round(gladauc4[1], digits=3)))+plotTheme2()






    ## BERG ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~


 berg4<- ggplot(bergtestProbs4, aes(x = Probs, fill = as.factor(Outcome))) + 
  geom_density() +
  facet_grid(Outcome ~ .) +
  scale_fill_manual(values = palette2) +
  labs(x = "Late Over 2 Mins", y = "Density of probabilities",
       title = "BERG Model 4: Distribution of Predicted Probabilities by Actual Outcome",
       caption= "WEATHER has stop lags") +
  theme(strip.text.x = element_text(size = 18),
        legend.position = "none")+plotTheme2()

 
 bergtestProbs4.thresholds <- 
  iterateThresholds(data=bergtestProbs4, observedClass = Outcome, 
                    predictedProbs = Probs)

bergtestProbs4.thresholds<-bergtestProbs4.thresholds%>%arrange(Rate_TP,Rate_TN) ## 0.56 identified


bergtestProbs4 <- 
  bergtestProbs4 %>%
  mutate(predOutcome  = as.factor(ifelse(bergtestProbs4$Probs > 0.56 , 1, 0)))








bergauc4<-pROC::auc(bergtestProbs4$Outcome, bergtestProbs4$Probs) #0.7437



bergroc.4<- ggplot(bergtestProbs4, aes(d = as.numeric(Outcome), m = Probs)) +
  geom_roc(n.cuts = 50, labels = FALSE, colour = "#a81010") +
  style_roc(theme = theme_grey) +
  geom_abline(slope = 1, intercept = 0, size = 1.5, color = 'grey') +
  labs(title = "ROC Curve - BERG Model 4", subtitle = paste("AUC:", round(bergauc4[1], digits=3)))+plotTheme2()





#plot_grid(glad4, berg4, nrow = 2)



```

```{r PREDICTIONS5, warning=FALSE, message=FALSE, include=FALSE, echo=TRUE, results='hide'}

##MODELS 4


#### Setting up Predictions FOR JUST Weather and Stoplag-----

    ## GLAD

gladtestProbs5<- data.frame(Outcome = as.factor(gladTestW$y2_numeric),
                         Probs = predict(gladModel5, gladTestW, type="response"))

    ## BERG

bergtestProbs5 <- data.frame(Outcome = as.factor(bergTestW$y2_numeric),
                         Probs = predict(bergModel5, bergTestW, type="response"))



#### FIGURE OUT WHAT THRESH with plot and iterate fn -----




## TEST PROBS PLOT **MODEL 3cW -- to figure out what threh**


    ## GLAD ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~


 glad5 <- ggplot(gladtestProbs5, aes(x = Probs, fill = as.factor(Outcome))) + 
  geom_density() +
  facet_grid(Outcome ~ .) +
  scale_fill_manual(values = palette2) +
  labs(x = "Late Over 2 Mins", y = "Density of probabilities",
       title = "GladStone Model 4: Distribution of Predicted Probabilities by Actual Outcome",
       caption= "WEATHER has stop lags") +
  theme(strip.text.x = element_text(size = 18),
        legend.position = "none")+plotTheme2()

 
 gladtestProbs5.thresholds <- 
  iterateThresholds(data=gladtestProbs5, observedClass = Outcome, 
                    predictedProbs = Probs)

gladtestProbs5.thresholds<-gladtestProbs5.thresholds%>%arrange(Rate_TP,Rate_TN) ## 0.47 identified



gladtestProbs5 <- 
  gladtestProbs5 %>%
  mutate(predOutcome  = as.factor(ifelse(gladtestProbs5$Probs > 0.47 , 1, 0)))







gladauc5<- pROC::auc(gladtestProbs5$Outcome, gladtestProbs5$Probs) 



gladroc.5<- ggplot(gladtestProbs5, aes(d = as.numeric(Outcome), m = Probs)) +
  geom_roc(n.cuts = 50, labels = FALSE, colour = "#a81010") +
  style_roc(theme = theme_grey) +
  geom_abline(slope = 1, intercept = 0, size = 1.5, color = 'grey') +
  labs(title = "ROC Curve - GLAD Model 4", subtitle = paste("AUC:", round(gladauc5[1], digits=3)))+plotTheme2()






    ## BERG ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~


 berg5<- ggplot(bergtestProbs5, aes(x = Probs, fill = as.factor(Outcome))) + 
  geom_density() +
  facet_grid(Outcome ~ .) +
  scale_fill_manual(values = palette2) +
  labs(x = "Late Over 2 Mins", y = "Density of probabilities",
       title = "BERG Model 4: Distribution of Predicted Probabilities by Actual Outcome",
       caption= "WEATHER has stop lags") +
  theme(strip.text.x = element_text(size = 18),
        legend.position = "none")+plotTheme2()

 
 bergtestProbs5.thresholds <- 
  iterateThresholds(data=bergtestProbs5, observedClass = Outcome, 
                    predictedProbs = Probs)

bergtestProbs5.thresholds<-bergtestProbs5.thresholds%>%arrange(Rate_TP,Rate_TN) ## 0.56 identified


bergtestProbs5 <- 
  bergtestProbs5 %>%
  mutate(predOutcome  = as.factor(ifelse(bergtestProbs5$Probs > 0.56 , 1, 0)))








bergauc5<-pROC::auc(bergtestProbs5$Outcome, bergtestProbs5$Probs) #



bergroc.5<- ggplot(bergtestProbs5, aes(d = as.numeric(Outcome), m = Probs)) +
  geom_roc(n.cuts = 50, labels = FALSE, colour = "#a81010") +
  style_roc(theme = theme_grey) +
  geom_abline(slope = 1, intercept = 0, size = 1.5, color = 'grey') +
  labs(title = "ROC Curve - BERG Model 4", subtitle = paste("AUC:", round(bergauc5[1], digits=3)))+plotTheme2()





#plot_grid(glad5, berg5, nrow = 2)



```

```{r allPredPlot}


plot_grid( glad1, berg1, glad2, berg2, glad3, berg3, glad4, berg4, glad5, berg5, nrow = 5)
plot_grid( gladroc.1, bergroc.1, gladroc.2, bergroc.2, gladroc.3, bergroc.3, gladroc.4, bergroc.4, gladroc.5, bergroc.5,nrow = 5)

```

## Visuals --- SOME OLD SOME STILL USEFUL

```{r resultsbar}




gladthresh <- gladtestProbs5.thresholds%>%filter(Threshold == .47)%>%dplyr::select(contains("Rate"), Accuracy)%>%mutate(line="Gladstone Branch") %>%gather(Variable, Value, -line)

bergthresh<- bergtestProbs4.thresholds%>%filter(Threshold == .56)%>%dplyr::select(contains("Rate"), Accuracy)%>%mutate(line="Bergen Co. Line") %>%gather(Variable, Value, -line)

gladbergthresh<-rbind(gladthresh, bergthresh)


resutlsbar <- gladbergthresh%>%
    ggplot(aes(Variable, Value, fill = line), colour= "white") +
      geom_bar(aes(fill = line), position = "dodge", stat = "identity") +
      scale_fill_manual(values = palette2b) +
      labs(title="Model Results",
           #subtitle = " ", 
           x = "Outcome",y = "Rate") +
      plotTheme2() + theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position = "bottom") 

resultsbar

```

```{r MAPs}
### MAPS ------



## PREPPING DATAFRAMES   
    
    ## GLAD 8am and 12pm~~~~


mapglad8<- gladGEOM%>%dplyr::filter(hour == 13 & week ==2)%>% mutate(weekday = fct_reorder(weekday,  daynumeric))%>%st_transform(4326)
mapglad12<- gladGEOM%>%dplyr::filter(hour == 5 & week ==2)%>% mutate(weekday = fct_reorder(weekday, daynumeric))%>%st_transform(4326)


rbg <- st_coordinates(mapglad8)
rbg2 <- st_coordinates(mapglad12)

mapglad8<- mapglad8%>%mutate(lat= rbg[, 2], long =  rbg[, 1])
mapglad12<- mapglad12%>%mutate(lat= rbg2[, 2], long =  rbg2[, 1])


     ## BERG  8am and 12pm~~~~


mapberg8<- bergGEOM%>%dplyr::filter(hour == 13 & week ==2)%>% mutate(weekday = fct_reorder(weekday, daynumeric))%>%st_transform(4326)

mapberg12<- bergGEOM%>%dplyr::filter(hour == 5 & week ==2)%>% mutate(weekday = fct_reorder(weekday, daynumeric))%>%st_transform(4326)


rb <- st_coordinates(mapberg8)
rb2 <- st_coordinates(mapberg12)

mapberg8<- mapberg8%>%mutate(lat= rb[, 2], long =  rb[, 1])
mapberg12<- mapberg12%>%mutate(lat= rb2[, 2], long =  rb2[, 1])



## TRYING TO GET A GODDAMN BASE MAP THAT DOESN"T LOOK LIKE SHITE

library(ggmap)
#install.packages("rstudioapi")
library(rstudioapi)
ggmap::register_google(key = "AIzaSyBCWh3md7doMjJzQQJZSfvyTFnbknsm6Fs") ##<-- mykeys 
#devtools::install_github("mikey-harper/ggmapstyles")
library(ggmapstyles)


nameless<- "https://snazzymaps.com/style/24115/nameless"     ##<---- these are all the diff base maps I've tried 
grays<- "https://snazzymaps.com/style/55/subtle-greyscale-map"
subtle<- "https://snazzymaps.com/style/19/subtle"
ultra<-"https://snazzymaps.com/style/396899/ultrasimple"
simple<- "https://snazzymaps.com/style/83357/simple"
bg<- "https://snazzymaps.com/style/121205/blank-bluegreyish"
vector<- "https://snazzymaps.com/style/38830/vector"
min<- "https://snazzymaps.com/style/76687/minimal"
blank<- "https://snazzymaps.com/style/220191/blank-background"
assass<- "https://snazzymaps.com/style/72543/assassins-creed-iv"
vint<-"https://snazzymaps.com/style/14/vintage"
old<-"https://snazzymaps.com/style/46616/old-style-minimal-with-highways"

spotB = 'Paterson, New Jersey'
mapB <- get_snazzymap(center = 'Paterson, New Jersey', 
                     mapRef = old,   ###   <----------------------pick one, save it to a var, and put that var here
                     zoom=9)    ### <------- if u make this numb. smaller, we will  lose data points for th bergmap

mapG <- get_snazzymap(center = 'South Orange, New Jersey', 
                     mapRef = old,   ###   <----------------------pick one, save it to a var, and put that var here
                     zoom=10)




#ggmap(map) ### <---- preveiew it with this 


pBERG <- ggmap(mapB, darken = 0.6) ## <---- then save this map to a var 

pGLAD<- ggmap(mapG, darken = 0.6)

p2 <- get_map(spot, zoom=10, maptype = "toner-background", style = 'style=feature:landscape.natural.terrain|visibility:simplified') ##<---- other route that's not really working 

p3<-ggmap(p2)



### ACTUALLY MAPPING ------


trialmap<-p + geom_point(data = mapberg, aes(x = long, y = lat))

  ###  BERG 8am ~~

bergMAP8am<-pBERG + geom_point(data = mapberg8,
          shape=21, color= 'grey10', alpha = 0.8,
          aes(x = long, y = lat, size = q5(lateM),
              fill= q5(lateM)))+
  scale_size_manual(name = "Minutes Late",
                    labels = qBr(mapberg8, "lateM"),
                     values= c(1,2,3,4,5))+
  scale_fill_brewer(
    type = "seq",
    palette = "PuBu", ## <-----------------------if you change this then you need to change it below too
    direction = 1,
    aesthetics = "fill", 
    guide= "none"
  )+
  labs(title = "Bergen Co Line: Minutes Late By Stop 8:00 AM Hour ET")+ 
       #subtitle = "By Tract, Boston 2013-2018",
       #caption = "Figure 3.1")+
  guides(size = guide_legend(override.aes = list(fill = brewer.pal(5, name="PuBu")) ##<------ here!
    ))+
      facet_wrap(~ weekday, ncol=7)+mapTheme2()

    ###  BERG 12pm ~~


bergMAP12<- pBERG+geom_point(data = mapberg12,
                        shape=21, color= 'grey10', alpha = 0.8,
          aes(x = long, y = lat, size = q5(lateM),
              fill= q5(lateM)))+
  scale_size_manual(name = "Minutes Late",
                    labels = qBr(mapberg12, "lateM"),
                     values= c(1,2,3,4,5))+
  scale_fill_brewer(
    type = "seq",
    palette = "PuBu",
    direction = 1,
    aesthetics = "fill", 
    guide= "none"
  )+
  labs(title = "Bergen Co Line: Minutes Late By Stop 12:00 PM Hour ET")+ 
       #subtitle = "By Tract, Boston 2013-2018",
       #caption = "Figure 3.1")+
  guides(size = guide_legend(override.aes = list(fill = brewer.pal(5, name="PuBu"))
    ))+
      facet_wrap(~ weekday, ncol=7)+mapTheme2()




    ### GLAD Map 8 ~~~ 




gladMAP8<- pGLAD + geom_point(data = mapglad8, shape=21, color= 'grey10', alpha = 0.8,
          aes(x = long, y = lat, size = q5(lateM),
              fill= q5(lateM)))+
  scale_size_manual(name = "Minutes Late",
                    labels = qBr(mapglad8, "lateM"),
                     values= c(1,2,3,4,5))+
  scale_fill_brewer(
    type = "seq",
    palette = "PuBu",
    direction = 1,
    aesthetics = "fill", 
    guide= "none"
  )+
  labs(title = "Gladstone Branch: Minutes Late By Stop 8:00 AM Hour ET")+
       #subtitle = "By Tract, Boston 2013-2018",
       #caption = "Figure 3.1")+
  guides(size = guide_legend(override.aes = list(fill = brewer.pal(5, name="PuBu"))
    ))+
      facet_wrap(~ weekday, ncol = 5)+mapTheme2()





gladMAPnoon<- pGLAD + geom_point(data = mapglad12,
          shape=21, color= 'grey10', alpha = 0.8,
          aes(x = long, y = lat, size = q5(lateM),
              fill= q5(lateM)))+
  scale_size_manual(name = "Minutes Late",
                    labels = qBr(mapglad12, "lateM"),
                     values= c(1,2,3,4,5))+
  scale_fill_brewer(
    type = "seq",
    palette = "PuBu",
    direction = 1,
    aesthetics = "fill", 
    guide= "none"
  )+
  labs(title = "Gladstone Branch: Minutes Late By Stop 12:00 PM Hour ET")+ 
       #subtitle = "By Tract, Boston 2013-2018",
       #caption = "Figure 3.1")+
  guides(size = guide_legend(override.aes = list(fill = brewer.pal(5, name="PuBu"))
    ))+
      facet_wrap(~ weekday, ncol = 5)+mapTheme2()

```

```{r LAGPLOTS}
###### LAG PLOTS -----



## GLAD CON'T FEATS




gladFEATdata <-glad.weather.panel%>%
  filter(week == 2) %>% dplyr::select( late, 
                                       #stop_sequence, 
                                        onestoplag,
                                        #hour, 
                                        lagHour,
                                        lag2Hours,
                                        lag3Hours) %>%gather(Variable, Value, -late) %>%
  mutate(Variable = fct_relevel(Variable, "onestoplag","lagHour", "lag2Hours",  "lag3Hours"))


gladFEATcorrelation <-
  group_by(gladFEATdata, Variable) %>%
    summarize(correlation = round(cor(Value, late, use = "complete.obs"), 2)) 


#93afdc


gladFEATplot <-ggplot(gladFEATdata, aes(Value,late)) +
  geom_point(size = 0.1, color="#93afdc") +
  geom_text(data = gladFEATcorrelation, aes(label = paste("r =", round(correlation, 2))),
            x=-Inf, y=Inf, vjust = 1.5, hjust = -.1) +
  geom_smooth(method = "lm", se = FALSE, colour = "#a81010") +
  facet_wrap(~Variable, ncol = 4, scales = "free") +
  labs(title = "Gladstone Branch: Train Delays as a Function of Contiuous Variables",
       subtitle = "One Week in 2019") +
  plotTheme2()









## BERG CON'T FEATS

bergFEATdata <-berg.weather.panel%>%
  filter(week == 2) %>% dplyr::select(late,
                                        #stop_sequence, 
                                        onestoplag,
                                        #hour, 
                                        #toSigStop, ## the to.Pennbinary var was  colinar but the to isn't IDK why
                                        lagHour,
                                        lag2Hours,
                                        lag3Hours) %>%
  gather(Variable, Value, -late) %>%
  mutate(Variable = fct_relevel(Variable, "onestoplag","lagHour", "lag2Hours",  "lag3Hours"))


bergFEATcorrelation <-
  group_by(bergFEATdata, Variable) %>%
    summarize(correlation = round(cor(Value, late, use = "complete.obs"), 2)) 


#93afdc


bergFEATplot <-ggplot(bergFEATdata, aes(Value,late)) +
  geom_point(size = 0.1, color="#93afdc") +
  geom_text(data = bergFEATcorrelation, aes(label = paste("r =", round(correlation, 2))),
            x=-Inf, y=Inf, vjust = 1.5, hjust = -.1) +
  geom_smooth(method = "lm", se = FALSE, colour = "#a81010") +
  facet_wrap(~Variable, ncol = 4, scales = "free") +
  labs(title = "Bergen Co. Line: Train Delays as a Function of Contiuous Variables",
       subtitle = "One Week in 2019") +
  plotTheme2()



### BOTH

plot_grid(gladFEATplot, bergFEATplot, nrow=2, ncol=1 )


## these are bad and don't show anything SQRT WIND -----------

plotData.lag <-glad.weather.panel%>%
  filter(week == 2) %>%
  dplyr::select(contains("SQRT"), late) %>%
  gather(Variable, Value, -late) %>%
  mutate(Variable = fct_relevel(Variable, "SQRTlag1Hour1wind","SQRTlag2Hourswind",
                                          "SQRTlag3Hoursrain",  "SQRTlag4Hoursrain","SQRTlag12Hoursrain","SQRTlag1dayrain"))


correlation.lag <-
  group_by(plotData.lag, Variable) %>%
    summarize(correlation = round(cor(Value, late, use = "complete.obs"), 2)) 





LAGplot <-ggplot(plotData.lag, aes(Value,late)) +
  geom_point(size = 0.1) +
  geom_text(data = correlation.lag, aes(label = paste("r =", round(correlation, 2))),
            x=-Inf, y=Inf, vjust = 1.5, hjust = -.1) +
  geom_smooth(method = "lm", se = FALSE, colour = "#a81010") +
  facet_wrap(~Variable, ncol = 2, scales = "free") +
  labs(title = "Train Delays as a Function of SQRT Wind Lag Delays",
       subtitle = "One Week in 2019") +
  plotTheme2()




```

```{r bar, fig.width=10, fig.height=12}


 #f2fdff
glad.origin <- glad.weather.panel %>%
  group_by(from) %>% 
  summarize(lateness = mean(late)) %>% mutate(from = fct_reorder(from, lateness)) %>%
    ggplot(aes(lateness, from)) + geom_bar(stat = "identity",  color = NA, fill= "#a81010") +
      labs(title="Does Lateness Vary by Stop Origin",
           subtitle="Gladstone Branch",
           x="Mean seconds late", y="Origin Stop") +
  scale_y_discrete(expand = expansion(mult = c(.02, .02)))+
  scale_x_continuous(expand = expansion(mult = c(0, 0.02)))+
     plotTheme2()



berg.origin <- berg.weather.panel %>%
  group_by(from) %>% 
  summarize(lateness = mean(late)) %>% mutate(from = fct_reorder(from, lateness)) %>%
    ggplot(aes(lateness, from)) + geom_bar(stat = "identity",  color = NA, fill= "#a81010") +
      labs(#title="Does Lateness Vary by Stop Origin",
           subtitle="Bergen Co. Line",
           x="Mean seconds late", y="Origin Stop") +
  scale_y_discrete(expand = expansion(mult = c(.02, .02)))+
  scale_x_continuous(expand = expansion(mult = c(0, 0.02)))+
     plotTheme2()




plot_grid(glad.origin, berg.origin, nrow=1, align = "h")


```
